\documentclass[margin,line]{res}


\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
\setlength{\pdfpagewidth}{\paperwidth}
\setlength{\pdfpageheight}{\paperheight}

% list1 is small indent
% list2 is big indent
% list3 is no indent

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.4in}}}{\end{list}}
\newenvironment{list3}{
  \begin{list}{}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0in}}}{\end{list}}

\usepackage[dvipsnames]{xcolor}

\usepackage[unicode=true]{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Cole Brokamp},
            pdftitle={Cole Brokamp CV},
            colorlinks=true,
            citecolor  = blue!80!black,
            urlcolor   = blue!80!black,
            linkcolor  = blue!80!black,
            pdfborder={0 0 0}
            }


\begin{document}

\name{Cole Brokamp \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3in}p{4in}}
Division of Biostatistics and Epidemiology & {\it Voice:}  (513) 518-5121 \\
Cincinnati Children's Hospital Medical Center & {\it E-mail:}  cole.brokamp@gmail.com\\
Cincinnati, OH 45229 USA  & {\it Website:} www.colebrokamp.com \\
\end{tabular}


\section{\sc Personal Statement}
I am an environmental and population health scientist trained at the
intersection of biostatistics, epidemiology, and geoinformatics in order to
advance precision public health. My work has focused on using
machine learning and causal inference methods with ``big spatial data'' to
estimate the effect of environmental exposures on pediatric health
outcomes. Specifically, my interest lies in the
interaction of these urban exposures with individual- and community-level
socioeconomic characteristics in order to to identify subpopulations of children
who are more susceptible to environmental health problems and inform targeted
interventions. I have specialized myself in the areas of machine learning and geoinformatics and their applications to large environmental and
clinical datasets. My early career work was dedicated to furthering exposure science methodology in
order to bring more precise exposure assessment tools to environmental health
studies. Furthermore, I have developed a novel approach and
accompanying software package called DeGAUSS which allows for user-friendly
attachment of geospatial variables to existing research cohorts and within
multi-site studies where sharing of private health information like residential
addresses is not feasible.

I have previously collaborated with Dr. Hall on
several projects, including the Ohio Opioid Analytics Project and automated
integration of geomarkers within the Mother Infant Data Hub (MIDH).
Specifically, we published a manuscript describing the causal impact of
community deprivation on hospital utilization during the first year of life by
geocoding and estimating community factors for mother-infant dyad pairs linked
through billing records, electronic health records, and birth certificates. I
look forward to contributing to the MAT-LINK project by creating and
implementing geomarker assessment tools that can be used across the multi-site network.


\section{\sc Education}

{\bf Cincinnati Children's Hospital Medical Center}, Cincinnati, Ohio USA \\
\vspace*{-.1in}
\begin{list1}
\item[]Postdoctoral Research Fellow, Biostatistics \& Epidemiology, 2016 -- 2017
\end{list1}

{\bf University of Cincinnati}, Cincinnati, Ohio USA \\
\vspace*{-.1in}
\begin{list1}
\item[]Ph.D., Biostatistics and Bioinformatics, 2016
\end{list1}

{\bf University of Cincinnati}, Cincinnati, Ohio USA\\
\vspace*{-.1in}
\begin{list1}
\item[]B.S., Biomedical Engineering, 2010
\end{list1}


\section{\sc Academic Experience}

{\bf Cincinnati Children's Hospital Medical Center}\\
{\bf University of Cincinnati Department of Pediatrics}\\
Division of Biostatistics \& Epidemiology\\
\vspace*{-.1in}
\begin{list1}
    \item[] Assistant Professor, 2017 - present
\end{list1}


\section{\sc Selected Publications}

\textbf{Cole Brokamp}, Jeffrey R. Strawn, Andrew F. Beck, Pat Ryan.
Pediatric Psychiatric Emergency Department Utilization and Fine
Particulate Matter: A Case-Crossover Study. \emph{Environmental Health
  Perspectives}. 127(9). 2019.
\href{https://s3.amazonaws.com/colebrokamp-website/publications/Brokamp_EHP_2019.pdf}{\emph{Download}}.

Erica Andrist, \textbf{Cole Brokamp}, Stuart Taylor, Carley Riley,
Andrew Beck. Neighborhood Poverty and Pediatric Intensive Care Use.
\emph{Pediatrics}. 2019.

\textbf{Cole Brokamp}, Andrew F. Beck, Neera K. Goyal, Patrick Ryan,
James M. Greenberg, Eric S. Hall. Material Community Deprivation and
Hospital Utilization During the First Year of Life: An Urban
Population-Based Cohort Study. \emph{Annals of Epidemiology}. 30. 37-43.
2019.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Brokamp_AoE_2019.pdf}{\emph{Download}}.

Juliana Madzia, Patrick Ryan, Kimberly Yolton, Zana Percy, Nick Newman,
Grace LeMasters, \textbf{Cole Brokamp}. Residential Greenspace Is
Associated with Childhood Behavioral Outcomes. \emph{Journal of
  Pediatrics}. 2018.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Madzia_JPeds_2018.pdf}{\emph{Download}}.

Lauren C. Riney, \textbf{Cole Brokamp}, Andrew F. Beck, Wendy Pomerantz,
Hamilton Schwartz, Todd A. Florin. Emergency Medical Services
Utilization is Associated with Community Deprivation in Children.
\emph{Prehospital Emergency Care}. Online ahead of print. 2018.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Riney_PrehospitalEmergencyCare_2018.pdf}{\emph{Download}}.

\textbf{Cole Brokamp}, Roman Jandarov, Monir Hossain, Patrick Ryan.
Predicting Daily Urban Fine Particulate Matter Concentrations Using
Random Forest. \emph{Environmental Science \& Technology}. 52 (7).
4173-4179. 2018.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Brokamp_EST_2018_onlineaheadofprint.pdf}{\emph{Download}}.

\textbf{Cole Brokamp}. DeGAUSS: Decentralized Geomarker Assessment for
Multi-Site Studies. \emph{Journal of Open Source Software}. 2018.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Brokamp_JOSS_2018.pdf}{\emph{Download}}.

Andrew F. Beck, Carley L. Riley, Stuart Taylor, \textbf{Cole Brokamp},
Robert S. Kahn. Toward a Culture of Health in Hospitals: Pervasive
population disparities in inpatient bed-day rates across conditions and
subspecialties. \emph{Health Affairs}. 37(4). 551-559. 2018.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Beck_HealthAffairs_2018.pdf}{\emph{Download}}.

\textbf{Cole Brokamp}, Chris Wolfe, Todd Lingren, John Harley, Patrick
Ryan. Decentralized and Reproducible Geocoding and Characterization of
Community and Environmental Exposures for Multi-Site Studies.
\emph{Journal of American Medical Informatics Association}. 25(3).
309-314. 2017.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Brokamp_JAMIA_2017.pdf}{\emph{Download}}.

\textbf{Cole Brokamp}, Andrew F. Beck, Louis Muglia, Patrick Ryan.
Combined Sewer Overflow Events and Childhood Emergency Department
Visits: A Case-Crossover Study. \emph{Science of the Total Environment}.
607-608. 1180-1187. 2017.
\href{http://colebrokamp-website.s3.amazonaws.com/publications/Brokamp_STOTEN_2017.pdf}{\emph{Download}}.

\textbf{Cole Brokamp}, Grace LeMasters, Patrick Ryan. Residential
mobility impacts exposure assessment and community socioeconomic
characteristics in longitudinal epidemiology studies. \emph{Journal of
  Exposure Science and Environmental Epidemiology}. 26(4). 428-34. 2016.
\href{http://colebrokamp-website.s3.amazonaws.com/publications/Brokamp_JESEE_2016.pdf}{\emph{Download}}.

\section{\sc Selected Grant Support}

\textbf{ECHO Opportunities and Infrastructure Fund Award}\\
\emph{Decentralized and Reproducible Geomarker Assessment for Multi-Site
  Studies}\\
Brokamp, PI (09/01/2019 - 08/31/2021)\\
This award will work towards building geospatial exposure assessment
computing tools for utilizing high resolution spatiotemporal gridded
datasets within ECHO.\\
Role: PI

\textbf{Internal Processes and Methods Award - Center for Clinical \&
  Translational Science \& Training}\\
\emph{Using Machine Learning to Supplement Electronic Health Record
  databases with Individual Socioeconomic Status}\\
Brokamp, PI (9/1/17 - 6/30/20)\\
Retrospective epidemiological studies are often created using electronic
health record databases. Although these records are ``wide'', they are
not ``deep'' with respect to individual level demographic data. We
propose a novel machine learning based approach that uses open city and
auditor databases to predict individual level income and family
socioeconomic status. This will solve the urgent problem of
unconfounding for individual SES in the execution of EHR based
research.\\
Role: PI

\end{resume}

\vfill

\hfill \textit{Last updated: \today}

\end{document}




